Time slice analyses

### 2017-12-18 analyses/02-time-slice-analyses.Rmd
Minor tidying of code
Reran full data

2. Equally sized time bins. 
    i. Where the *duration* of the bin is equal to the median duration of the stratigraphic period.
    ii. Where the *number* of bins is equal to the number of stratigraphic periods.
    iii. Where the *number* of bins is either 2, 5, 10, 15, or 20.

3. Time slicing. 
    i. Where the *interval* between slices is equal to the median duration of the stratigraphic period.
    ii. Where the *number* of slices is equal to the number of stratigraphic periods.
    iii. Where the *number* of slices is either 2, 5, 10, 15, or 20.

@@

## Loading the tree
## See "01-extract-data-for analyses.Rmd" for how we cleaned these
tree <- read.nexus(paste0("../data/processed/tree.", slug, ".tre"))
## Add root age (max tree age date)
tree$root.time <- max(tree.age(tree)[, 1])

>>>>

2. Equally sized time bins. 
    i. Where the *duration* of the bin is equal to the median duration of the stratigraphic period.
    ii. Where the *number* of bins is equal to the number of stratigraphic periods.

3. Time slicing. 
    i. Where the *interval* between slices is equal to the median duration of the stratigraphic period.
    ii. Where the *number* of slices is equal to the number of stratigraphic periods.

@@

## Loading the tree
## See "01-extract-data-for analyses.Rmd" for how we cleaned these
tree <- read.nexus(paste0("../data/processed/tree.", slug, ".tre"))

## Remove the taxa not present in the tree but in the FADLAD
absent_in_tree <- clean.data(FADLAD, tree)$dropped_rows
if(!any(is.na(absent_in_tree))) {
    FADLAD <- FADLAD[-match(absent_in_tree, rownames(FADLAD)),]
}

## Getting the tree ages
tree_ages <- tree.age(tree)

## Scaling with the latest FADLAD
tree$root.time <- max(tree_ages[,1] + min(FADLAD[,2]))
